Adopting agile in the large: motivations, success factors and challenges

### 2014-04-16 journal/article.tex
Business areas; Initial state

In several cases there were more than one primary study presenting the
transformation of the same organization. Even if the transformation of a single
organization was described in many studies all sources that passed the inclusion
criterial were included. Studies presenting the same organization were treated
as one unit so that we could gain as much insight from each organization as
possible. There were also a few papers that presented multiple case studies, and
in those cases we treated each studied organization individually. As a result 42
unique organizations were identified in the primary studies.

@@

@@

\begin{table}
    \begin{tabular}{ l r r r }
        \toprule
        Method    &  Reported in studies   \\
        \midrule
        Scrum            &  28 \\
        XP               &  5  \\
        Scrum with XP    &  6  \\
        Scrum with Lean  &  7  \\
        Other            &  4  \\
        Not specified    &  4  \\
        \bottomrule
    \end{tabular}
    \caption{Agile methods reported in the transformed organization}
    \label{table:agile_methods}
\end{table}

The agile methods reported being used in the transformed organizations are
summarized in table \ref{table:agile_methods}. The most prevalent method was
Scrum, which was the sole agile method mentioned in 28 studies. The second most
mentioned agile method was Extreme Programming (XP). Lean software development
was mentioned in some studies, although combined to Scrum in all cases. Other
agile methods mentioned were Unified Process, ADM, and Rapid Application
Development.

@@

>>>>

In several cases there were more than one primary study presenting the
transformation of the same organization. Even if the transformation of a single
organization was described in many studies all sources that passed the inclusion
criterial were included. Studies presenting the same organization were treated
as one unit so that we could gain as much insight from each organization as
possible. There were also a few papers that presented multiple case studies, and
in those cases we treated each studied organization individually. As a result 42
unique organizations were identified in the primary studies. We use the word
\textit{case} to refer to the individual case organizations, and the word
\textit{study} to refer to the primary studies.

@@

The business areas of the case organizations are presented in table
\ref{table:businessareas}. Different business areas were represented somewhat
evenly. Online services was the largest group, including companies
providing software as a service solutions for businesses, online media players
for consumers, online services for consumers, and communication software for
businesses. The second largest group was telecommunications, including companies
such as British Telecom, Cisco, Ericsson, and Nokia Siemens Networks. The third
largest group was enterprise management solution providers with products for
business process management, project protfolio management, and facility
management.

\begin{table}
    \begin{tabular}{ l r r r }
        \toprule
        Business area    &  Case organizations   \\
        \midrule
		Online services for consumers and business  &  9  \\
		Telecommunications                          &  7  \\
		Enterprise management                       &  5  \\
		Banking and financial services              &  4  \\
		Healthcare                                  &  3  \\
		IT services                                 &  2  \\
		Government                                  &  1  \\
		Information security                        &  1  \\
		Not specified                               & 10  \\
        \bottomrule
    \end{tabular}
    \caption{Business areas of case organizations in primary studies}
    \label{table:businessareas}
\end{table}

@@

\begin{table}
    \begin{tabular}{ l r r r }
        \toprule
        Method    &  Reported in studies   \\
        \midrule
        Scrum            &  25 \\
        XP               &  4  \\
        Scrum with XP    &  5  \\
        Scrum with Lean  &  6  \\
        Other            &  4  \\
        Not specified    &  1  \\
        \bottomrule
    \end{tabular}
    \caption{Agile methods reported in the transformed organization}
    \label{table:agilemethods}
\end{table}

The agile methods reported being used in the transformed organizations are
summarized in table \ref{table:agilemethods}. The most prevalent method was
Scrum, which was the sole agile method mentioned in 28 studies. The second most
mentioned agile method was Extreme Programming (XP). Lean software development
was mentioned in some studies, although combined to Scrum in all cases. Other
agile methods mentioned were Unified Process, ADM, and Rapid Application
Development. In one case the agile method was not named.

@@

\subsection{Transformation process}

\subsubsection{The initial state of the organization}

We investigated the initial state of the case organizations before the
transformation. The typical initial process model was described as waterfall, as
stated in 25 cases. In several cases the authors characterized the initial state
of the organization as ``\quote{traditional}''. CMMI was presented as a driver
for the original process in 4 cases. Other process models the studies named were
RUP [P19], Prince2 [P51], and Macroscope [P14]. In 9 cases the initial state was
not described.

The old model was described in most cases briefly and in a neutral sentiment.
Waterfall development in general was referred to as ``\quote{traditional,
plan-based methods}'' [P25], ``\quote{traditional phase-based approach}'' [P36],
or ``\quote{old fashioned process driven waterfall}'' [P23]. Korhonen [P25]
referred to the model presented by Royce \cite{Royce1970} when describing the
initial state.

In some cases specifics of the old model was criticized. The characteristics of
the old process models were described as having ``\quote{many gates and
sign-offs required by upper levels of management}'' [P9], ``\quote{lot of
bureaucracy in project management and a strict hierarchy of requirements
communication}'' [P39], and ``\quote{project managers typically used a
command-and-control philosophy}'' [P44].

In a few cases the initial process model was less rigid, and closer to the agile
model that was to be introduced. Examples of such loose process models were
described: ``\quote{The choice of development methodology is one of any number
of degrees of freedom granted to teams at Amazon. Development teams are expected
to solve their problems in the best way possible}'' [P3], ``\quote{the R&D group
leveraged a loose, waterfall-based process with an entrepreneurial culture}''
[P16]. Some organizations had even signs of agile development on team level
although the surrounding organization operated in a waterfall fashion. This was
described as ``\quote{Agile and Scrum were increasingly popular and emerging at
a grass-roots level, at a corporate level Yahoo! still embraced a more
traditional product development process}'' [P10], and ``\quote{some teams had
applied scrum on the team level, despite the surrounding organization that was
working with a waterfall software engineering model}'' [P26].

In a few cases the organization initailly lacked strict process. For instance
Long described the initial state in the following way: ``\quote{Project scope
was in constant flux. Well-meaning market and product owners routinely inserted
new requirements during product development.}'' [P30].

Some authors described the developement being originally organized in silos. For
instance Ranganath describes that ``\quote{Teams operated in silos.
Collaboration, shared purpose and ownership for outcomes were hard to find}''
[P40].
